When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-27 doc/paper/vpd_et_paper.tex
okay going to change plotting around

An additional concern is that the LAI term may in fact be some function of $D$, in which case the dependence would need to be accounted for when taking the derivative. Figure \ref{lai_vpd_fig} plots the jount distrivution of LAI and VPD, and shows that LAI is very weakly a function of VPD. Given this weak dependence, we argue that Equation \ref{d_et} is a valid approxiamtion for ET response to $D$.

@@

%%n
 \begin{linenomath*}
 \begin{equation}
 \end{equation}
 \end{linenomath*}

>>>>

An additional concern is that the LAI term may in fact be some function of $D$, in which case the dependence would need to be accounted for when taking the derivative. Figure \ref{lai_vpd_fig} plots the joint distrivution of LAI and VPD, and shows that LAI is very weakly a function of VPD. Given this weak dependence, we argue that Equation \ref{d_et} is a valid approxiamtion for ET response to $D$.

@@

In Term 1, $\frac{P}{T} \propto \rho$, so this should vary little relative to $g_a$ and $\Delta$.  $\gamma$ should also be relatively constant, So the scaling term, Term 1, should be primarily a function of $g_a$ and temperature (though the function $\Delta$). Figure \ref{scale_vary} shows how the magnitude of the scaling varies with $T$ and $g_a$.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig04.pdf}
\caption{Variability of Term 1 for each PFT. Each colored line correspondes to a different aerodynamic resistance.}
\label{lai_vpd_fig}
\end{figure}

%%
 \begin{linenomath*}
 \begin{equation}
 \end{equation}
 \end{linenomath*}
